A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2020-11-13 kobakian-cook.Rmd
small changes to conclusion

<!-- Summarise paper, usability -->
A choropleth map display is the current common practice for spatial data visualisation. As the choropleth map display relies on the geographic shapes, it does not effectively present the density of the population in small geographic areas. The common solution to enhance the communication of spatial distributions is to incorporate the population values as a cartogram or another alternative map display. Many alternative map displays do not work well for Australia due to the large rural geographic space between the densely populated capital cities. The administrative boundaries may also distract from the statistics communicated using colour due to the small size of some areas.
This paper provides an algorithm for Australia called the hexagon tile map.

@@

This algorithm should  be general enough to apply to other countries and problems

@@

<!-- , limitiations, where it might not work -->

This algorithm has only been tested using single countries, and does not consider definite borders of countries. While the buffer allows extension beyond the furthest centroids, there is no mechanism to protect the borders and ensure centroids are placed within the geographic borders of a country.

>>>>

This paper has described a new algorithm for creating an alternative display. 
This paper provides an algorithm for Australia called the hexagon tile map.

<!-- Summarise paper, usability, sound like a summary, not introduction -->
A choropleth map display is the current common practice for spatial data visualisation. As the choropleth map display relies on the geographic shapes, it does not effectively present the density of the population in small geographic areas. The common solution to enhance the communication of spatial distributions is to incorporate the population values as a cartogram or another alternative map display. Many alternative map displays do not work well for Australia due to the large rural geographic space between the densely populated capital cities. The administrative boundaries may also distract from the statistics communicated using colour due to the small size of some areas.

@@

@@

<!-- limitiations, where it might not work -->

This algorithm should  be general enough to apply to other countries and problems.
XXX 
This algorithm has only been tested using single countries, and does not consider definite borders of countries. While the buffer allows extension beyond the furthest centroids, there is no mechanism to protect the borders and ensure centroids are placed within the geographic borders of a country.
